\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-20 paper.qmd
Added flow for triangulation

When $k=2$, the number of bins along the $x$ and $y$ axes, $b_1$ and $b_2$ should computed by accounting ${r_1, r_2}$, offset along the axes, and height ($h_b$), width ($w_b$).

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($h_b$), width ($w_b$). The starting coordinates $(x_s, y_s)$ mark the lower left of the grid. <!--We deliberately separate out the creation of the hexagonal grid from the mapping of points on the grid.-->
Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to.

@@

#### Triangulating centroids

>>>>

When $k=2$, the number of bins along the $x$ and $y$ axes, $b_1$ and $b_2$ is computed by accounting ${r_1, r_2}$, offset along the axes ($q_1$, $q_2$), and height ($h_b$), width ($w_b$) of a regular hexagon.

($b_1 = \frac{r_1 + q_1}{w_b}$, $b_2 = \frac{r_2 + q_2}{0.75 \times h_b}$): $0.75 \times h_b$ acommodate to have the tesselation without spacing.

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($h_b$), width ($w_b$).

When $k=2$,

The starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$ and $b_2$.

<!--We deliberately separate out the creation of the hexagonal grid from the mapping of points on the grid.-->
Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

@@

#### Generating edges

computes a set of simplices such that no data points of X are contained in any circumspheres of the simplices.

### 2024-04-20 paper.tex
Added flow for triangulation

When \(k=2\), the number of bins along the \(x\) and \(y\) axes, \(b_1\)
and \(b_2\) should computed by accounting \({r_1, r_2}\), offset along
the axes, and height (\(h_b\)), width (\(w_b\)).

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(h_b\)), width (\(w_b\)). The starting coordinates
\((x_s, y_s)\) mark the lower left of the grid. Each of the \kD{} points
will belong to a hexagonal bin. That is, for each
\(y \in \mathbfit{Y}\), we can (uniquely) identify the hexagon that the
point belongs to.

@@

\subsubsection{Triangulating centroids}\label{triangulating-centroids}

>>>>

When \(k=2\), the number of bins along the \(x\) and \(y\) axes, \(b_1\)
and \(b_2\) is computed by accounting \({r_1, r_2}\), offset along the
axes (\(q_1\), \(q_2\)), and height (\(h_b\)), width (\(w_b\)) of a
regular hexagon.

(\(b_1 = \frac{r_1 + q_1}{w_b}\),
\(b_2 = \frac{r_2 + q_2}{0.75 \times h_b}\)): \(0.75 \times h_b\)
acommodate to have the tesselation without spacing.

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(h_b\)), width (\(w_b\)).

When \(k=2\),

The starting coordinates \((s_1, s_2)\) mark the lower left of the grid.
This is the bottom left bin centroid. By starting from there, points are
generated to fill the grid accounting \(b_1\) and \(b_2\).

Each of the \kD{} points will belong to a hexagonal bin. That is, for
each \(y \in \mathbfit{Y}\), we can (uniquely) identify the hexagon that
the point belongs to. This identification is done finding the nearest
bin centroid for the \kD{} points by considering the \kD{} Euclidean
distance.

@@

\subsubsection{Generating edges}\label{generating-edges}

computes a set of simplices such that no data points of X are contained
in any circumspheres of the simplices.
